Check Coverage

### 2020-06-22 analysis/merge_data.Rmd
clarify the NA scenarios for different species identification variables, make sure I'm excluding the appropriate one.

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(!study_id %in% c(195, 360), #exclude because they break
         !study_id %in% c(217, 327)) #exclude to get the file size smaller

@@

Let's also do the functions from BAT package
```{r}
#function for getting PCA axes with at least 95% coverage
axes95 <- function(mat){
  axes <- pco(mat)
  eigen <- axes$eig

  threshold <- sum(eigen[eigen > 0]) * 0.95

  sums <- cumsum(eigen)
  num_axes <- Position(function(x) x > threshold, sums)

  return(num_axes)
}

get_BAT_fd <- function(data, study, plot_num){
  require(BAT)

  data <- data %>%
    na.omit(id) %>%
    filter(study_id == study, plot == plot_num)

  #get PCA trait matrix
  trait_dist <- gower.dist(trait_mat)
  trait_pco <- pco(trait_dist, k = axes95(trait_dist))

  return(rownames(trait_pco$points) <- rownames)
  # fs::dir_create(paste0(here::here("data"), "/fd_output"))
  # 
  # #the convexhull c code creates an output file of vertices, in order to not have multiple threads writing
  # #to the same file we have to create individual working directories
  # tmp_dir <- paste0(here::here("data", "fd_output", "tmp"), "/tmp_", study, plot_num)
  # fs::dir_create(tmp_dir)
  # setwd(tmp_dir)
  # 
  # fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
  #   cbind(years, .) %>%
  #   mutate(study_id = unlist(study), plot = unlist(plot_num), trait_count = dim(trait_mat)[2]) %>%
  #   write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot_num, "_fd.tsv"))
  # 
  # setwd(here::here())
  # return(fd_out)
}

```

@@

#Correct FD for species richness

First for one study, 311
```{r}

glm_correction <- function(study, plot_num){
  model_data <- fd_table %>% filter(metric == "FRic", study_id == study, plot == plot_num)
  fit <- glm(value ~ richness, data = model_data)

  pred_vars <- model_data %>% 
    select(richness) %>% 
    distinct() %>%
    mutate(fric_pred = predict(fit, ., type = "response"))

  plot_data <- left_join(model_data, pred_vars) %>%
    mutate(fric_adj = value - fric_pred,
           fric_adj = ifelse(fric_adj > 0, fric_adj, 0))

  return(plot_data)
}

plot_data <- glm_correction(311, 1)

plot_data %>%
  ggplot() +
  geom_line(aes(x = year, y = value), color = "blue") +
  geom_line(aes(x = year, y = fric_pred), color = "red") +
  geom_line(aes(x = year, y = fric_adj), color = "black") +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  theme(legend.position = "none") +
  ylab("Fric")
```

>>>>

First pass at calculating FD metrics
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(!study_id %in% c(195, 360), #exclude because they break
         !study_id %in% c(217, 327)) #exclude to get the file size smaller

@@

@@
